---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# entsog

<!-- badges: start -->
<!-- badges: end -->

The goal of entsog is to wrap the ENTSO-G API.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("krose/entsog")
```
## Example

Here is how to get data. We load the relevant packages and extract the data from the api:

```{r example}
library(entsog)
library(tidyverse)

glimpse(eg_agg(countryKey = "DE"))
glimpse(eg_connectionpoints())

glimpse(eg_op(indicator = "Physical Flow", pointDirection = "DE-TSO-0001ITP-00096entry", from = Sys.Date() - 2, to = Sys.Date() +2, periodType = "hour"))

```


## Note

This if from Entso-G:

_... the API is publicly available, there are some restrictions in the
use of API to ensure that the limited resources of the ENTSOG TP are shared fairly with all TP
users. There is a timeout value on all queries to be 60 seconds. Additional filters should be
used such as data ranges, specific points, operators and/or indicators to return a successful
result set._
